\pkg{cpop}: Detecting Changes in Piecewise-Linear Signals

### 2022-12-05 latex/response.tex

\title{cpop: Detecting changes in piecewise-linear signals -- response to review and pre-screening comments}
\author{Paul Fearnhead and Daniel Grose}
\date{\today}

\documentclass[12pt]{article}

\usepackage[dvipsnames]{xcolor}

\begin{document}
\maketitle
\noindent
{\bf Response to pre-screening comments II }
\\

We have added spaces to the code to facilitate reading: with spaces before and after operators and after commas.

We believe the paper has commas after e.g. and i.e.

We believe we have used latex commands proglang, pkg and code throughout.

We believe all software packages have been cited as per the package instructions -- though most of these are to the original research papers, or papers in JSS, rather than a citation for the package itself.

All references are in title style.

\noindent
{\bf Response to pre-screening comments I }
\\

Thanks for the careful reading of our paper, and the helpful comments. We apologise for not fully meeting the journal's stylistic requirements. We have now updated the paper as requested:
\begin{itemize}
\item[(i)] We have replaced the use of cat() with message() in the code.
\item[(ii)] We have used the third (rather than first) argument of system.time when calculating the plot comparing timings of methods.
\item[(iii)] We have corrected the incorrect code chunks for loops etc. (i.e., replacing R $>$ with +).
\item[(iv)] The section and subsection titles are now in sentence style; citations are in title style.
\item[(v)] We have added commas after i.e. and e.g. and ensured we have used prog, code and proglang throughout.
\item[(vi)] Where they have citation info, we have ensured that all R packages are cited per this information.
\end{itemize}

### 2022-12-05 latex/article.tex
Add files via upload

Despite these challenges, there are three methods developed specifically for detecting changes-in-slope: Trend-filtering \citep{kim2009ell_1,tibshirani2014adaptive} which minimises the residual sum of squares of fit to the data plus an $L_1$ penalty on the changes-in-slope; NOT \citep{baranowski2016narrowest} that repeatedly performs a test for a single change-in-slope on subsets of the data and combines the results using the narrowest-over-threshold procedure; and CPOP \citep{fearnhead2019detecting} which uses a novel variant of dynamic programming to minimise the residual sum of squares plus an $L_0$ penalty, i.e. a constant penalty for adding each change. The difference between the $L_1$ penalty of trend-filtering and the $L_0$ penalty of CPOP is important in practice: as the former allows one to fit a single change in slope with multiple changes of the same sign. This can lead to either over-fitting the number of changes, or, if a large enough penalty is used to detect the changes accurately, over-smoothing the mean function: see the bottom row of plots in Figure \ref{fig:intro} for an example. The main difference between CPOP and NOT is that the former fits all changes simultaneously. See \cite{fearnhead2019detecting} for an empirical comparison of the three methods.

@@

cpop(y, x = 1:length(y) - 1, grid = x, beta = 2*log(length(y)), 
    sd =  sqrt(mean(diff(diff(y))^2)/6), minseglen = 0, 

@@

\item \code{beta} -  A positive real value for the penalty, $\beta$ in (\ref{eq:penalisedcost2}), incurred for adding a changepoint. The larger the penalty, the fewer changepoints will be detected. The default value is \code{beta = 2*log(length(y))}.
\item \code{sd} - Estimate of residual standard deviation. Can be a single numerical value if it is the same for all data points, or a vector of $n$ values for the case of varying standard deviation. The default value is \code{sd = sqrt(mean(diff(diff(y))**2)/6)}.

@@

R> res <- cpop(y, x, beta = 2*log(length(y)), sd = 0.8)

@@

The function \code{changepoints(object)}
creates a data frame containing the locations of the changepoints in terms of the their $x$-values.
%\newpage
\begin{CodeChunk}
\begin{CodeInput}
R> changepoints(res)
\end{CodeInput}
\begin{CodeOutput}
  location
1       22
2       52
3       95
\end{CodeOutput}
\end{CodeChunk}
%
%
%The function \code{cost(object)} calculates the penalised cost of a model fitted by \code{cpop} using the residual sum of squares and the penalty values.
%\begin{CodeChunk}
%\begin{CodeInput}
%R> cost(res)
%\end{CodeInput}
%\begin{CodeOutput}
%[1] 47.39048
%\end{CodeOutput}
%\end{CodeChunk}
%
%
The function \code{estimate(object, x = object@x, ...)} with argument,
 \code{x}, that specifies the $x$-values at which the fit is to be estimated, creates a data frame with two columns containing the locations \code{x} and the corresponding estimates $\hat{y}$. The default value for \code{x} is the vector of $x$ locations at which the cpop object was defined.
  % \item \code{...} - For compatability with existing S4 generic methods. \end{itemize}%
%\subsubsection{example}
\begin{CodeChunk}
\begin{CodeInput}
R> estimate(res, x = c(0.1 ,2.7 ,51.6))
\end{CodeInput}
\begin{CodeOutput}
   x     y_hat
1  0.1 0.1473350
2  2.7 0.7289166
3 51.6 2.9473390
\end{CodeOutput}
\end{CodeChunk}
%
%
The function \code{fitted(object)} creates a data frame containing the endpoint coordinates for each line segment fitted between the detected
changepoints. The data frame also contains the gradient and intercept values for each segment and the corresponding residual sum of squares (RSS).
%\subsubsection{example}
\begin{CodeChunk}
\begin{CodeInput}
R> fitted(res)
\end{CodeInput}
\begin{CodeOutput}
  x0       y0  x1       y1     gradient   intercept      RSS
1  1 0.147335  22 4.844725  0.223685242 -0.07635023 10.07761
2 22 4.844725  52 2.717661 -0.070902123  6.40457180 10.38813
3 52 2.717661  95 7.303644  0.106650750 -2.82817758 25.09463
4 95 7.303644 200 7.563413  0.002473995  7.06861408 61.78303
\end{CodeOutput}
\end{CodeChunk}
%
%
Finally, the function \code{residuals(object)}  creates a single column matrix containing the residuals.
\newpage
%\subsubsection{example}
\begin{CodeChunk}
\begin{CodeInput}
R> head(residuals(res))
\end{CodeInput}
\begin{CodeOutput}
           [,1]
[1,] -0.4484981
[2,]  0.1758944
[3,] -0.6632084
[4,]  1.2578339
[5,]  0.2215302
[6,] -0.7221359
\end{CodeOutput}
\end{CodeChunk}
 %
 %

@@

\begin{CodeChunk}
\begin{CodeInput}
R> x <- (1:200)^(2)/(200)
R> changepoints <- c(0, 25, 50, 100)
R> change.slope <- c(0.2, -0.3, 0.2, -0.1)
R> sd <- 0.8
R> y <- simchangeslope(x, changepoints, change.slope, sd)
\end{CodeInput}
\end{CodeChunk}

To analyse the data we use \code{cpop} as before. (The only difference is that for evenly spaced data one can omit the \code{x} argument -- but it must be included for unevenly spaced data.)
\begin{CodeChunk}
\begin{CodeInput}
R> res <- cpop(y, x, beta = 2*log(length(y)), sd = 0.8)
\end{CodeInput}
\end{CodeChunk}
%
%
Figure \ref{fig:cpop-example-uneven} shows a plot of the simulated data and estimated changepoints and mean function.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> x <- 1:200
R> sd <- x/100
R> y <- simchangeslope(x, changepoints, change.slope, sd))
\end{CodeInput}
\end{CodeChunk}
%
%
Here the values of \code{changepoints} and \code{change.slope} are as before.

It is interesting to compare two estimates of the changepoints, one where we assume a fixed noise standard deviation, and one where we assume the true noise standard deviation. For the former it is natural to set this value so the the average variance of the noise is correct. 
\begin{CodeChunk}
\begin{CodeInput}
R> res <- cpop(y, x, beta = 2*log(length(y)), sd = sqrt(mean(sd^2)))
R> res.true <- cpop(y, x, beta = 2*log(length(y)), sd = sd)
\end{CodeInput}
\end{CodeChunk}
Here \code{res} contains the results where we assume a fixed noise standard deviation, and \code{res.true} where we use the true values. Figure \ref{fig:cpop-example-heterogeneous} shows the results -- and we can see that wrongly assuming homogeneous noise leads to detecting two false positive changepoints in regions where the noise variance is above what was assumed.

@@

To see this we implemented the scheme for a data set with $n=6400$ and a fixed segment size of 200.  We initially ran \code{cpop} with a grid with potential changes allowed every 16 observations.
%\newpage
\begin{CodeChunk}
\begin{CodeInput}
R> x <- 1:6400
R> y <- simchangeslope(x, changepoints = 0:31*200, 
+ change.slope = c(0.05, 0.1*(-1)^(1:(31))), sigma = 1)
\end{CodeInput}
\end{CodeChunk}

We use a smaller value for the penalty due to the smaller grid size, and the fact that this is a preliminary step to find roughly where the changes are: so the key is to avoid missing changes. Spurious changes can still be removed when we perform our final run of \code{cpop}. 
\begin{CodeChunk}
\begin{CodeInput}
R> res.coarse <- cpop(y, x, grid = 1:399*16, beta = 2*log(400), sd = 1)
\end{CodeInput}
\end{CodeChunk}

In our example we find 38 changepoints with this coarse grid. We then introduce a finer grid around these putative changes: our new grid includes all $x$-values within 8 of each putative changepoint.
\begin{CodeChunk}
\begin{CodeInput}
R> cps <- unlist(changepoints(res.coarse))
R> grid <- NULL
R> for(i in 1:length(cps)) {
+   grid <- c(grid, cps[i]+(-7):8)
+ }
R> res.fine <- cpop(y, x, grid, beta = 2*log(length(x)), sd = 1)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> changepoints <- c(0, 25, 50, 100)
R> change.slope <- c(0.2, -0.3, 0.2, -0.1)
R> x <- 1:200
R> mu <- simchangeslope(x, changepoints, change.slope, sigma = 0)
R> y <- mu + rt(length(x), df = 4)
\end{CodeInput}
\end{CodeChunk}

We then estimated the changepoint locations both without a minimum segment length, and with minimum segment lengths of 10, 30 and 40. To run \code{cpop} with a minimum segment length of 10:
\begin{CodeChunk}
\begin{CodeInput}
R> res.min <- cpop(y, x, beta = 2*log(length(y)),
+  minseglen = 10, sd = sqrt(2) )
\end{CodeInput}
\end{CodeChunk}
The argument \code{sd = sqrt(2)} is because $t_4$ distributed noise has a variance of 2.
%
%\begin{figure}
%\begin{minipage}{.5\linewidth}
%\centering
%{\includegraphics[scale=.5]{figures/cpop-minseg1.pdf}}
%\end{minipage}%
%\begin{minipage}{.5\linewidth}
%\centering
%{\includegraphics[scale=.5]{figures/cpop-minseg2.pdf}}
%\end{minipage}%
%\newline
%\begin{minipage}{.5\linewidth}
%\centering
%{\includegraphics[scale=.5]{figures/cpop-minseg3.pdf}}
%\end{minipage}%
%\begin{minipage}{.5\linewidth}
%\centering
%{\includegraphics[scale=.5]{figures/cpop-minseg4.pdf}}
%\end{minipage}%
%\centering
%\includegraphics{figures/cpop-example-uneven.pdf}
%\caption{Results of analysing data with $t_4$ noise with no minimum segment length (top left) and minimum segment lengths of 10 (top right), 30 (bottom left) and 40 (bottom right). In each plot we show data (grey dots), true mean (blue dashed line), true changepoints (blue vertical dashed lines), estimated mean (black line) and estimated changepoints (red vertical liens)}
%\label{fig:cpop-minseg}
%\end{figure}
%
%
\begin{figure}
\centering
{\includegraphics[scale=.5]{figures/cpop_minseg_ggplot.pdf}}
\caption{Results of analysing data with $t_4$ noise with no minimum segment length (top left) and minimum segment lengths of 10 (top right), 30 (bottom left) and 40 (bottom right). In each plot we show data (grey dots), true mean (blue dashed line), true changepoints (blue vertical dashed lines), estimated mean (black line) and estimated changepoints (red vertical liens)}
\label{fig:cpop-minseg}
\end{figure}
%
%
Results from CPOP with different minimum segment lengths are shown in Figure \ref{fig:cpop-minseg}. If we do not impose a minimum segment length, then we estimate 11 changepoints, including three cluster of changes that overfit to the noise. By imposing a minimum segment length of 10 we avoid the over-fitting. For this example, the computational cost of running \code{cpop} with the minimum segment length is about 15 times larger than when we do not assume a minimum segment length.

@@

The idea of CROPS is that it allows a penalised cost method to be implemented for all penalty values in an interval. This is implemented within the \pkg{cpop} package by the function:
\begin{CodeInput}
cpop.crops(y, x = 1:length(y), grid = x, beta_min = 1.5*log(length(y)),
  beta_max = 2.5*log(length(y)), sd =  sqrt(mean(diff(diff(y))^2)/6), 
  minseglen = 0, prune.approx = FALSE)
\end{CodeInput}
The arguments of \code{cpop.crops} are identical to those of \code{cpop} except that, rather than specifying a single penalty value (\code{beta}), the range of penalty values to be used is specified by \code{beta_min} and \code{beta_max}, which fix the smallest and largest penalty value to be used. The output is an instance of an S4 class that contains details of all segmentations found by minimising the penalised cost for some penalty value in the interval between \code{beta_min} and \code{beta_max}.

@@

Details of the segmentations can be obtained using \code{segmentations(res.crops) }. This gives a matrix with one row for each of the segmentations, and each row contains a value of $\beta$ that gives that segmentation, the corresponding unpenalised cost, the penalised cost, the number of changepoints, and then the list of ordered changepoints. 
%
%
We can also obtain a list with the output from \code{cpop} corresponding to each segmentation, with \code{models( res.crops )}. For example, one approach to choose a segmentation from the output from \code{cpop.crops} is to find the segmentation that minimises a cost under a model where we assume the noise variance is unknown \citep{fryzlewicz2014wild},
\[
 n \log \left( \frac{1}{n} \sum_{i=1}^n \left(y_i-\hat{f}(x_i)\right)^2
\right) + 2 K \log n.
\]
Here $\hat{f}$ is the estimated mean function and $K$ is the number of changepoints. This can be calculated as follows.
\begin{CodeChunk}
\begin{CodeInput}
R> models <- cpop.crops.models(res.crops)
R> M <- length(models)
R> BIC <- rep(NA, M)
R> ncps <- segmentations(res.crops )[,4]
R> n <- length(y)
R> for(j in 1:M) {
+   BIC[i] <- n*log(mean((residuals(models[[j]]))^2)) + 2*ncps[i]*log(n)
+ }
\end{CodeInput}
\end{CodeChunk}
This uses that the fourth column of the matrix \code{segmentations( res.crops )} stores the number of changepoints in each segmentation, and that we can calculate $y_i - \hat{f}(x_i)$ using the \code{residual} function evaluated for the corresponding entry of \code{cpop.crops.models(res.crops)}. The segmentation which has the smallest value of \code{BIC} is shown in Figure \ref{fig:crops.cpopA}, and shows that this correctly chooses the segmentation with three changes.

@@

We simulated data with $n=500$ data points and $10$ equally spaced changepoints.
\begin{CodeChunk}
\begin{CodeInput}
R> n <- 500
R> x <- 1:n
R> mu <- simchangeslope(x, changepoints = 45*0:10, 
+  change.slope = c(0.15, 0.3*(-1)^(1:10)), sd = 0)
R> epsilon <- rnorm(n+2)
R> y <- mu + (epsilon[1:n] + epsilon[2:(n+1)] + epsilon[3:(n+2)])/sqrt(3)
\end{CodeInput}
\end{CodeChunk}
The noise is MA(3), and we simulate the data by first calculating the mean function, \code{mu}, and then adding the MA(3) noise.

@@

Interest lies in estimating the rate of decay of the log-spectra against log-wavenumber. We can do this by removing the first three data points (where the spectra is increasing) and then using \code{cpop} to fit a piecewise-linear curve to the remaining data. We perform an initial run of \code{cpop} assuming an estimated homogeneous noise variance on the data from August from the 2000 run.
\begin{CodeChunk}
\begin{CodeInput}
R> data("wavenumber_spectra")
R> x <- log(wavenumber_spectra[-(1:3),1])
R> y <- log(wavenumber_spectra[-(1:3),4])
R> grid <- seq(from = min(x), to = max(x), length = 200)

R> sig2 <- mean(diff(diff(y))^2)/6 
R> res <- cpop(y, x, grid, sd = sqrt(sig2), 
+              minseglen = 0.09, beta = 2*log(200))
\end{CodeInput}
\end{CodeChunk}
Here we estimate the noise variance, \code{sig2}, based on the variance of the double difference of the data. For regions where the mean is linear and the data is evenly spaced, taking the double difference will lead to a mean zero process. If the noise is IID with variance $\sigma^2$ then the double-differenced process will have a marginal variance that is $6\sigma^2$. Thus our estimate is the empirical mean of the square of the double-difference data divided by 6. The original data is evenly spaced in in terms of wavenumber, but as we take logs, \code{x} is unevenly spaced: so this estimator will be biased in our setting. However it will give a reasonable ball-park figure for an initial run of \code{cpop} -- the residuals from which can then be used to get a better estimate of the noise variance. We use a evenly spaced grid for possible change-point locations. To avoid the potential for adding multiple changepoints between two observations, we set a minimum segment length of 0.09 (as the largest distance between consecutive \code{x} values is 0.08).

>>>>

Despite these challenges, there are three methods developed specifically for detecting changes-in-slope: Trend-filtering \citep{kim2009ell_1,tibshirani2014adaptive} which minimises the residual sum of squares of fit to the data plus an $L_1$ penalty on the changes-in-slope; NOT \citep{baranowski2016narrowest} that repeatedly performs a test for a single change-in-slope on subsets of the data and combines the results using the narrowest-over-threshold procedure; and CPOP \citep{fearnhead2019detecting} which uses a novel variant of dynamic programming to minimise the residual sum of squares plus an $L_0$ penalty, i.e., a constant penalty for adding each change. The difference between the $L_1$ penalty of trend-filtering and the $L_0$ penalty of CPOP is important in practice: as the former allows one to fit a single change in slope with multiple changes of the same sign. This can lead to either over-fitting the number of changes, or, if a large enough penalty is used to detect the changes accurately, over-smoothing the mean function: see the bottom row of plots in Figure \ref{fig:intro} for an example. The main difference between CPOP and NOT is that the former fits all changes simultaneously. See \cite{fearnhead2019detecting} for an empirical comparison of the three methods.

@@

cpop(y, x = 1:length(y) - 1, grid = x, beta = 2 * log(length(y)), 
    sd =  sqrt(mean(diff(diff(y)) ^ 2) / 6), minseglen = 0, 

@@

\item \code{beta} -  A positive real value for the penalty, $\beta$ in (\ref{eq:penalisedcost2}), incurred for adding a changepoint. The larger the penalty, the fewer changepoints will be detected. The default value is \code{beta = 2 * log(length(y))}.
\item \code{sd} - Estimate of residual standard deviation. Can be a single numerical value if it is the same for all data points, or a vector of $n$ values for the case of varying standard deviation. The default value is \code{sd = sqrt(mean(diff(diff(y)) ** 2) / 6)}.

@@

R> res <- cpop(y, x, beta = 2 * log(length(y)), sd = 0.8)

@@

The function \code{changepoints(object)}
creates a data frame containing the locations of the changepoints in terms of the their $x$-values.
%\newpage
\begin{CodeChunk}
\begin{CodeInput}
R> changepoints(res)
\end{CodeInput}
\begin{CodeOutput}
  location
1       22
2       52
3       95
\end{CodeOutput}
\end{CodeChunk}
%
%
%The function \code{cost(object)} calculates the penalised cost of a model fitted by \code{cpop} using the residual sum of squares and the penalty values.
%\begin{CodeChunk}
%\begin{CodeInput}
%R> cost(res)
%\end{CodeInput}
%\begin{CodeOutput}
%[1] 47.39048
%\end{CodeOutput}
%\end{CodeChunk}
%
%
The function \code{estimate(object, x = object@x, ...)} with argument,
 \code{x}, that specifies the $x$-values at which the fit is to be estimated, creates a data frame with two columns containing the locations \code{x} and the corresponding estimates $\hat{y}$. The default value for \code{x} is the vector of $x$ locations at which the cpop object was defined.
  % \item \code{...} - For compatability with existing S4 generic methods. \end{itemize}%
%\subsubsection{example}
\begin{CodeChunk}
\begin{CodeInput}
R> estimate(res, x = c(0.1, 2.7, 51.6))
\end{CodeInput}
\begin{CodeOutput}
   x      y_hat
1  0.1 -0.0539817
2  2.7  0.5275999
3 51.6  2.7460223

\end{CodeOutput}
\end{CodeChunk}
%
%
The function \code{fitted(object)} creates a data frame containing the endpoint coordinates for each line segment fitted between the detected
changepoints. The data frame also contains the gradient and intercept values for each segment and the corresponding residual sum of squares (RSS).
%\subsubsection{example}
\begin{CodeChunk}
\begin{CodeInput}
R> fitted(res)
\end{CodeInput}
\begin{CodeOutput}
  x0       y0  x1       y1     gradient   intercept      RSS
1  1 0.147335  22 4.844725  0.223685242 -0.07635023 10.07761
2 22 4.844725  52 2.717661 -0.070902123  6.40457180 10.38813
3 52 2.717661  95 7.303644  0.106650750 -2.82817758 25.09463
4 95 7.303644 200 7.563413  0.002473995  7.06861408 61.78303
\end{CodeOutput}
\end{CodeChunk}
%
%
Finally, the function \code{residuals(object)}  creates a single column matrix containing the residuals.
\newpage
%\subsubsection{example}
\begin{CodeChunk}
\begin{CodeInput}
R> head(residuals(res))
\end{CodeInput}
\begin{CodeOutput}
           [,1]
[1,] -0.4484981
[2,]  0.1758944
[3,] -0.6632084
[4,]  1.2578339
[5,]  0.2215302
[6,] -0.7221359
\end{CodeOutput}
\end{CodeChunk}
 %
 %

@@

\begin{CodeChunk}
\begin{CodeInput}
R> x <- (1:200) ^ 2 / 200
R> changepoints <- c(0, 25, 50, 100)
R> change.slope <- c(0.2, -0.3, 0.2, -0.1)
R> sd <- 0.8
R> y <- simchangeslope(x, changepoints, change.slope, sd)
\end{CodeInput}
\end{CodeChunk}

To analyse the data we use \code{cpop} as before. (The only difference is that for evenly spaced data one can omit the \code{x} argument -- but it must be included for unevenly spaced data.)
\begin{CodeChunk}
\begin{CodeInput}
R> res <- cpop(y, x, beta = 2 * log(length(y)), sd = 0.8)
\end{CodeInput}
\end{CodeChunk}
%
%
Figure \ref{fig:cpop-example-uneven} shows a plot of the simulated data and estimated changepoints and mean function.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> x <- 1:200
R> sd <- x / 100
R> y <- simchangeslope(x, changepoints, change.slope, sd)
\end{CodeInput}
\end{CodeChunk}
%
%
Here the values of \code{changepoints} and \code{change.slope} are as before.

It is interesting to compare two estimates of the changepoints, one where we assume a fixed noise standard deviation, and one where we assume the true noise standard deviation. For the former it is natural to set this value so the the average variance of the noise is correct. 
\begin{CodeChunk}
\begin{CodeInput}
R> res <- cpop(y, x, beta = 2 * log(length(y)), sd = sqrt(mean(sd ^ 2)))
R> res.true <- cpop(y, x, beta = 2 * log(length(y)), sd = sd)
\end{CodeInput}
\end{CodeChunk}
Here \code{res} contains the results where we assume a fixed noise standard deviation, and \code{res.true} where we use the true values. Figure \ref{fig:cpop-example-heterogeneous} shows the results -- and we can see that wrongly assuming homogeneous noise leads to detecting two false positive changepoints in regions where the noise variance is above what was assumed.

@@

To see this we implemented the scheme for a data set with $n=6400$ and a fixed segment size of 200.  We initially ran \code{cpop} with a grid with potential changes allowed every 16 observations.
%\newpage
\begin{CodeChunk}
\begin{CodeInput}
R> x <- 1:6400
R> y <- simchangeslope(x, changepoints = 0:31 * 200, 
+ change.slope = c(0.05, 0.1 * (-1) ^ (1:31)), sd = 1)
\end{CodeInput}
\end{CodeChunk}

We use a smaller value for the penalty due to the smaller grid size, and the fact that this is a preliminary step to find roughly where the changes are: so the key is to avoid missing changes. Spurious changes can still be removed when we perform our final run of \code{cpop}. 
\begin{CodeChunk}
\begin{CodeInput}
R> res.coarse <- cpop(y, x, grid = 1:399 * 16, beta = 2 * log(400), sd = 1)
\end{CodeInput}
\end{CodeChunk}

In our example we find 38 changepoints with this coarse grid. We then introduce a finer grid around these putative changes: our new grid includes all $x$-values within 8 of each putative changepoint.
\begin{CodeChunk}
\begin{CodeInput}
R> cps <- unlist(changepoints(res.coarse))
R> grid <- NULL
R> for(i in 1:length(cps)) {
+   grid <- c(grid, cps[i] + (-7) : 8)
+ }
R> res.fine <- cpop(y, x, grid, beta = 2 * log(length(x)), sd = 1)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> changepoints <- c(0, 25, 50, 100)
R> change.slope <- c(0.2, -0.3, 0.2, -0.1)
R> x <- 1:200
R> y <- simchangeslope(x, changepoints, change.slope, 1.5) 
\end{CodeInput}
\end{CodeChunk}

We then estimated the changepoint locations both without a minimum segment length, and with minimum segment lengths of 10, 30 and 40. To run \code{cpop} with a minimum segment length of 10:
\begin{CodeChunk}
\begin{CodeInput}
R> res.min <- cpop(y, x, beta = 2 * log(length(y)),
+  minseglen = 10, sd = sqrt(2) )
\end{CodeInput}
\end{CodeChunk}
The argument \code{sd = sqrt(2)} is because $t_4$ distributed noise has a variance of 2.
%
%\begin{figure}
%\begin{minipage}{.5\linewidth}
%\centering
%{\includegraphics[scale=.5]{figures/cpop-minseg1.pdf}}
%\end{minipage}%
%\begin{minipage}{.5\linewidth}
%\centering
%{\includegraphics[scale=.5]{figures/cpop-minseg2.pdf}}
%\end{minipage}%
%\newline
%\begin{minipage}{.5\linewidth}
%\centering
%{\includegraphics[scale=.5]{figures/cpop-minseg3.pdf}}
%\end{minipage}%
%\begin{minipage}{.5\linewidth}
%\centering
%{\includegraphics[scale=.5]{figures/cpop-minseg4.pdf}}
%\end{minipage}%
%\centering
%\includegraphics{figures/cpop-example-uneven.pdf}
%\caption{Results of analysing data with $t_4$ noise with no minimum segment length (top left) and minimum segment lengths of 10 (top right), 30 (bottom left) and 40 (bottom right). In each plot we show data (grey dots), true mean (blue dashed line), true changepoints (blue vertical dashed lines), estimated mean (black line) and estimated changepoints (red vertical liens)}
%\label{fig:cpop-minseg}
%\end{figure}
%
%
\begin{figure}
\centering
{\includegraphics[scale=.5]{figures/cpop_minseg_ggplot.pdf}}
\caption{Results of analysing data with $t_4$ noise with no minimum segment length (top left) and minimum segment lengths of 10 (top right), 30 (bottom left) and 40 (bottom right). In each plot we show data (grey dots), true mean (blue dashed line), true changepoints (blue vertical dashed lines), estimated mean (black line) and estimated changepoints (red vertical liens)}
\label{fig:cpop-minseg}
\end{figure}
%
%
Results from CPOP with different minimum segment lengths are shown in Figure \ref{fig:cpop-minseg}. If we do not impose a minimum segment length, then we estimate 11 changepoints, including three cluster of changes that overfit to the noise. By imposing a minimum segment length of 10 we avoid the over-fitting. For this example, the computational cost of running \code{cpop} with the minimum segment length is about 6 times larger than when we do not assume a minimum segment length.

@@

The idea of CROPS is that it allows a penalised cost method to be implemented for all penalty values in an interval. This is implemented within the \pkg{cpop} package by the function:
\begin{CodeInput}
cpop.crops(y, x = 1:length(y), grid = x, beta_min = 1.5 * log(length(y)),
  beta_max = 2.5 * log(length(y)), sd =  sqrt(mean(diff(diff(y)) ^ 2) / 6), 
  minseglen = 0, prune.approx = FALSE)
\end{CodeInput}
The arguments of \code{cpop.crops} are identical to those of \code{cpop} except that, rather than specifying a single penalty value (\code{beta}), the range of penalty values to be used is specified by \code{beta_min} and \code{beta_max}, which fix the smallest and largest penalty value to be used. The output is an instance of an S4 class that contains details of all segmentations found by minimising the penalised cost for some penalty value in the interval between \code{beta_min} and \code{beta_max}.

@@

Details of the segmentations can be obtained using \code{segmentations(res.crops) }. This gives a matrix with one row for each of the segmentations, and each row contains a value of $\beta$ that gives that segmentation, the corresponding unpenalised cost, the penalised cost, the number of changepoints, and then the list of ordered changepoints. 
%
%
We can also obtain a list with the output from \code{cpop} corresponding to each segmentation, with \code{models( res.crops )}. For example, one approach to choose a segmentation from the output from \code{cpop.crops} is to find the segmentation that minimises a cost under a model where we assume the noise variance is unknown \citep{fryzlewicz2014wild},
\[
 n \log \left( \frac{1}{n} \sum_{i=1}^n \left(y_i-\hat{f}(x_i)\right)^2
\right) + 2 K \log n.
\]
Here $\hat{f}$ is the estimated mean function and $K$ is the number of changepoints. This can be calculated as follows.
\begin{CodeChunk}
\begin{CodeInput}
R> models <- cpop.crops.models(res.crops)
R> M <- length(models)
R> BIC <- rep(NA, M)
R> ncps <- segmentations(res.crops )[, 4]
R> n <- length(y)
R> for(j in 1:M) {
+   BIC[i] <- n * log(mean((residuals(models[[j]])) ^ 2)) + 
+             2 * ncps[i] * log(n)
+ }
\end{CodeInput}
\end{CodeChunk}
This uses that the fourth column of the matrix \code{segmentations( res.crops )} stores the number of changepoints in each segmentation, and that we can calculate $y_i - \hat{f}(x_i)$ using the \code{residual} function evaluated for the corresponding entry of \code{cpop.crops.models(res.crops)}. The segmentation which has the smallest value of \code{BIC} is shown in Figure \ref{fig:crops.cpopA}, and shows that this correctly chooses the segmentation with three changes.

@@

We simulated data with $n=500$ data points and $10$ equally spaced changepoints.
\begin{CodeChunk}
\begin{CodeInput}
R> n <- 500
R> x <- 1:n
R> mu <- simchangeslope(x, changepoints = 45 * 0:10, 
+  change.slope = c(0.15, 0.3 *  (-1) ^ (1 : 10)), sd = 0)
R> epsilon <- rnorm(n + 2)
R> y <- mu + (epsilon[1:n] + epsilon[2:(n + 1)] + 
+             epsilon[3:(n + 2)]) / sqrt(3)
\end{CodeInput}
\end{CodeChunk}
The noise is MA(3), and we simulate the data by first calculating the mean function, \code{mu}, and then adding the MA(3) noise.

@@

Interest lies in estimating the rate of decay of the log-spectra against log-wavenumber. We can do this by removing the first three data points (where the spectra is increasing) and then using \code{cpop} to fit a piecewise-linear curve to the remaining data. We perform an initial run of \code{cpop} assuming an estimated homogeneous noise variance on the data from August from the 2000 run.
\begin{CodeChunk}
\begin{CodeInput}
R> data("wavenumber_spectra")
R> x <- log(wavenumber_spectra[-(1:3), 1])
R> y <- log(wavenumber_spectra[-(1:3), 4])
R> grid <- seq(from = min(x), to = max(x), length = 200)
R> sig2 <- mean(diff(diff(y)) ^ 2) / 6 
R> res <- cpop(y, x, grid, sd = sqrt(sig2), 
+              minseglen = 0.09, beta = 2 * log(200))
\end{CodeInput}
\end{CodeChunk}
Here we estimate the noise variance, \code{sig2}, based on the variance of the double difference of the data. For regions where the mean is linear and the data is evenly spaced, taking the double difference will lead to a mean zero process. If the noise is IID with variance $\sigma^2$ then the double-differenced process will have a marginal variance that is $6\sigma^2$. Thus our estimate is the empirical mean of the square of the double-difference data divided by 6. The original data is evenly spaced in in terms of wavenumber, but as we take logs, \code{x} is unevenly spaced: so this estimator will be biased in our setting. However it will give a reasonable ball-park figure for an initial run of \code{cpop} -- the residuals from which can then be used to get a better estimate of the noise variance. We use a evenly spaced grid for possible change-point locations. To avoid the potential for adding multiple changepoints between two observations, we set a minimum segment length of 0.09 (as the largest distance between consecutive \code{x} values is 0.08).
